% vim:ft=tex

\section{Plenary}\label{80eeafc}

All the proofs and results I don't want to write twice.

\textbf{1.x.x)} Real analysis

\Definition{1.1.1}{Monotone sequences}\label{d5142a8}

A sequence $\{x_n\}$ is said to be \textbf{increasing} if $x_0\leq
	x_1\leq x_2\leq\ldots$ and \textbf{decreasing} if $x_0\geq x_1\geq
	x_2\geq\ldots$ and \textbf{monotone} if it is either increasing or
decreasing.

\Theorem{1.1.2}{Monotone convergence theorem}\label{ca25eb7}

If $\{x_n\}$ is monotone and bounded, then $\{x_n\}$ converges.

$$
	\lim_{n\to\infty}=\begin{cases}
		\sup\{x_n:n\in\N\} & \text{if $\{x_n\}$ is increasing} \\
		\inf\{x_n:n\in\N\} & \text{if $\{x_n\}$ is decreasing}
	\end{cases}
$$

\Theorem{1.1.3}{Monotone subsequence theorem}\label{dddb70e}

Every sequence has a monotone subsequence.

\begin{proof}
	\def\xn{\{x_n\}}

	Let $\xn$ be a sequence. We call a term $x_p$ a \textbf{peak term}
	of $\xn$ if
	$$x_p\geq x_n\quad(\forall n\geq p)$$

	That is, all terms after $x_p$ never go above $x_p$ again. Then
	there are only two cases:

	\textbf{Case 1:} $\xn$ has infinitely many peak terms.

	Then the subsequence formed by all the peak terms form a decreasing
	subsequence of $\xn$.

	\textbf{Case 2:} $\xn$ has finitely many peak terms.

	Let $x_{p_1},x_{p_2},\ldots,x_{p_j}$ be \textbf{all} the peak terms.

	Let $n_1=p_j+1$ be the first term after the last peak term.

	Since $x_{n_1}$ is not a peak term. $\implies\exists n_2>n_1$ such
	that $x_{n_1}<x_{n_2}$.

	Since $x_{n_2}$ is not a peak term, $\implies\exists n_3>n_2$ such
	that $x_{n_2}<x_{n_3}$.

	Continuing indefinitely, we can form an increasing subsequence
	$\{x_{n_k}\}$.
\end{proof}

\Theorem{1.1.4}{Bolzano-Weierstrass Theorem}

Every bounded sequence has a convergent subsequence.

\begin{proof}
	\def\xn{\{x_n\}}
	\def\xnk{\{x_{n_k}\}}

	Let $\xn$ be a bounded sequence. By the monotone subsequence
	theorem, $\xn$ has a monotone subsequence $\xnk$.

	Since $\xn$ is bounded, so is $\xnk$.

	Since $\xnk$ is both monotone and bounded, it follows from the
	\hyperref[ca25eb7]{monotone convergence theorem} that $\xnk$
	converges.
\end{proof}

% proof for MATH 378

\Theorem{1.1.5}{Monotone sequence with a convergent subsequence is
	convergent}\label{aaf3ba6}

Let $\{x_n\}$ be a monotone sequence with a subsequence $\{x_{n_k}\}$
that converges to $L$. Then $\{x_n\}$ converges to $L$.

\begin{proof}
	WLOG, assume that $\{x_n\}$ is decreasing.
	Given any $\epsilon>0$, we want to find a $N_\epsilon\in\N$ such that
	$$
		|x_n-L|<\epsilon\quad\forall(n\geq N_\epsilon)
	$$

	Since $\{x_{n_k}\}$ is decreasing and converges to $L$, we can find
	(and fix) a $k_\epsilon$ such that
	\begin{equation*}
		0<x_{n_k}-L<\epsilon\quad\forall(k\geq k_\epsilon)\tag*{($*$)}
	\end{equation*}
	So we take $N_\epsilon=n_{k_\epsilon}$. Then since $\{x_n\}$ is
	decreasing,
	$$
		x_n\leq x_{N_\epsilon}=x_{n_{k_\epsilon}}\quad\forall(n\geq N_\epsilon)
	$$
	Moreover, $L\leq x_n\leq x_{n_{k_\epsilon}}$, and hence
	$$0\leq x_n-L\leq x_{n_{k_\epsilon}}-L$$
	and from $(*)$, we have that this entire inequality $<\epsilon$, and hence
	$$0\leq x_n-L<\epsilon$$
	and finally
	$$|x_n-L|<\epsilon$$
\end{proof}

\Theorem{1.1.6}{Mean value theorem}

Let $f:[a,b]\to\R$ be continuous on the $[a,b]$, and differentiable on
$(a,b)$. Then there exists $c\in(a,b)$ such that
$$
	f'(c)=\frac{f(b)-f(a)}{b-a}
$$

Generalized to multiple variables, the mean value theorem can be
written as:

Let $f:[a,b]\to\R$, where $a,b\in\R^n$, and $[a,b]$ refers to the line
segment connecting $a$ and $b$, namely
$$
	[a,b]:=\{\lambda a+(1-\lambda)b\mid\lambda\in[0,1]\}
$$

Suppose $f$ is continuous on $[a,b]$ and differentiable on $(a,b)$.
Then there exists $c\in[a,b]$ such that
$$
	\nabla f(c)^T(b-a)=f(b)-f(a)
$$

In some arguments, we use $f:[x,x+td]\to\R$ and write that there
exists $\eta\in[x,x+td]$ such that
$$
	\nabla f(\eta)^Td=\frac{f(x+td)-f(x)}t
$$
